Something that is not PCADSC

### 2017-02-24 article/article_v0.01.tex
Typo 'eta' til '\eta'

\subsection{Principal component analysis - a very brief introduction}
Principal component analysis (PCA) allows us to decompose a data matrix consisting of $n$ observations of $d$ variables into $d$ orthogonal vectors of length $d$. This is in itself not very impressive nor useful. But PCA does not result in just any basis of the data matrix. The basis chosen using PCA has the very favorable property that each vector is chosen such that they maximize the accumulated explained variance. These vectors are usually denoted \textit{principal component scores} or simply \textit{principal components} and they are constructed as linear combinations of the variables in the dataset (or, equivalently, as projections of the data matrix). The coefficients of each variable in these projections are denoted \textit{loadings}. Let $S \in \RR^{d \times d}$ denote the empirical covariance matrix and let $X \in \RR^{n \times d}$ denote our observed data matrix. $d$ is the number of variables while $n$ is the number of observations. The deconstruction procedure then goes as follows:
\begin{enumerate}
\item The vector of loadings corresponding to the first principal component, $\eta_1 \in \RR^d$, is chosen such that the component explains as much variance as possible. More precisely, for any unit vector $u \in \RR^d$ we find that $\V(u^T X^T)$ is maximized when $u = \eta_1$. Let $\lambda_1 = \V(\eta_1^T X^T)$. 
\item The second vector of loadings is then chosen as $\eta_2 = \argmax_{u: \, u \perp \eta_1} \V(u^T X^T)$ and we again define $\lambda_2 := \V(\eta_2 X)$.
\item The third vector of loadings is $\eta_3 = \argmax_{u: \, u \perp \{\eta_1, \eta_2\}} \V(u^T X^T)$ and $\lambda_3 :=  \V(\eta_3^T X^T)$ \\
\vdots 
\item[\refstepcounter{enumi} $d$.] The $d$th vector of loadings is $\eta_d = \argmax_{u: \, u \perp \{eta_1, ..., \eta_{d-1}\}} \V(u^T X^T)$ and $\lambda_d = V(\eta_d^T X^T)$.
\end{enumerate}
The $\eta_i$s and $\lambda_i$s are determined uniquely (up to scaling) and they are given as the eigenvectors and eigenvalues of $S$, respectively. Moreover, we find that $X = \sum_{i=1}^d \eta_j \eta_j^T X$, so the procedure is really just a clever choice of rotation of the data, such that it is split up into vectors that are ordered by their variances, or more precisely, their variance contributions. We define the contribution to the total variance of the $k$th principal component as $\frac{\lambda_k}{tr(S)}$ and please note that, due to the properties of eigenvalue decomposition, $tr(S) = \sum_{i=1}^d \lambda_i$, which is the sum of the variances of the variables in the dataset.

>>>>

\subsection{Principal component analysis - a very brief introduction}
Principal component analysis (PCA) allows us to decompose a data matrix consisting of $n$ observations of $d$ variables into $d$ orthogonal vectors of length $d$. This is in itself not very impressive nor useful. But PCA does not result in just any basis of the data matrix. The basis chosen using PCA has the very favorable property that each vector is chosen such that they maximize the accumulated explained variance. These vectors are usually denoted \textit{principal component scores} or simply \textit{principal components} and they are constructed as linear combinations of the variables in the dataset (or, equivalently, as projections of the data matrix). The coefficients of each variable in these projections are denoted \textit{loadings}. Let $S \in \RR^{d \times d}$ denote the empirical covariance matrix and let $X \in \RR^{n \times d}$ denote our observed data matrix. $d$ is the number of variables while $n$ is the number of observations. The deconstruction procedure then goes as follows:
\begin{enumerate}
\item The vector of loadings corresponding to the first principal component, $\eta_1 \in \RR^d$, is chosen such that the component explains as much variance as possible. More precisely, for any unit vector $u \in \RR^d$ we find that $\V(u^T X^T)$ is maximized when $u = \eta_1$. Let $\lambda_1 = \V(\eta_1^T X^T)$. 
\item The second vector of loadings is then chosen as $\eta_2 = \argmax_{u: \, u \perp \eta_1} \V(u^T X^T)$ and we again define $\lambda_2 := \V(\eta_2 X)$.
\item The third vector of loadings is $\eta_3 = \argmax_{u: \, u \perp \{\eta_1, \eta_2\}} \V(u^T X^T)$ and $\lambda_3 :=  \V(\eta_3^T X^T)$ \\
\vdots 
\item[\refstepcounter{enumi} $d$.] The $d$th vector of loadings is $\eta_d = \argmax_{u: \, u \perp \{\eta_1, ..., \eta_{d-1}\}} \V(u^T X^T)$ and $\lambda_d = V(\eta_d^T X^T)$.
\end{enumerate}
The $\eta_i$s and $\lambda_i$s are determined uniquely (up to scaling) and they are given as the eigenvectors and eigenvalues of $S$, respectively. Moreover, we find that $X = \sum_{i=1}^d \eta_j \eta_j^T X$, so the procedure is really just a clever choice of rotation of the data, such that it is split up into vectors that are ordered by their variances, or more precisely, their variance contributions. We define the contribution to the total variance of the $k$th principal component as $\frac{\lambda_k}{tr(S)}$ and please note that, due to the properties of eigenvalue decomposition, $tr(S) = \sum_{i=1}^d \lambda_i$, which is the sum of the variances of the variables in the dataset.
